GRASS: Distinguishing Planet-induced Doppler Signatures from Granulation with a Synthetic Spectra Generator

### 2022-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

\input{captions/fig1.tex}

@@

\input{tables/spectroscopic.tex}

@@

\input{captions/fig2.tex}

@@

\input{captions/fig3.tex}

@@

\input{captions/fig4.tex}
\revise{To create synthetic spectra, \grass\ creates disk-resolved line profiles on a uniform spatial grid (as described in \S\ref{sec:resolved_disk}).} The \revise{ideal resolution of this spatial grid over the stellar surface would match that of the input observations. However, because the spatial resolution of the input observations was designed to approximate the typical angular area of supergranules and consequently varies with position on the disk (as described in \S\ref{subsec:input_data}), simulating an ideal grid is impractical.} Therefore, we choose \revise{a rectangular grid and set} $N$ \revise{(the number of grid cells along each Cartesian $xy$ direction in the sky plane) such that the area of the spatial grid cell matches the weighted-average area of the input data observations. Given the sizes of the elliptical oscillations described in \S\ref{subsec:input_data} and \citetalias{Lohner-Bottcher2018}, we compute $N^2\sim132^2$ as our optimized number of grid cells.} \par

@@

\subsection{Synthetic Line Depth and RV Variability} \label{sec:depth_var}
\input{captions/fig5.tex}

@@

\input{captions/fig6.tex}

@@

\input{captions/fig7.tex}

@@

\input{tables/observations.tex}

>>>>

% \input{captions/fig1.tex}

\begin{figure*}[htb!]
\gridline{\fig{figures/fig1a.pdf}{0.4\textwidth}{}}
          % \fig{figures/fig1b.pdf}{0.55\textwidth}{}}
\caption{Temporal and spatial variability in input bisectors encode turbulent granulation velocities. \textbf{Left:} To capture the line-of-sight variation observed in solar bisectors, observations were carried out at many discrete disk positions along each of the four solar limbs plus disk center. Figure adapted from Figure 1 of \citetalias{Lohner-Bottcher2018}. \textbf{Right:} Line bisectors differ in shape with both time and apparent position on the solar disk. From disk center ($\mu = 1$) to the limb ($\mu = 0$), bisectors transition from a distorted ``C"-shape to something more resembling a ``\textbackslash"-shape. This behavior results from the different viewing angles of convective granules along different lines of sight \citep[Figure 17.13 of ][]{Gray2008}. The solid, \revise{dashed, and dotted} lines trace the time-averaged bisector for each limb position. The shaded regions correspond to the $\pm1\sigma$ temporal variability of the bisectors at each limb position. Error bars in velocity are not shown; with an absolute wavelength calibration accuracy on order $\sim$$0.02$ m\AA\ ($\sim$1 $\ms$), the observed temporal variations are much larger than the typical uncertainty. \label{fig:one}}
\end{figure*}

@@

% \input{tables/spectroscopic.tex}
\begin{deluxetable*}{ccccccccccc}[htb!]
\tablecaption{Parameters for spectroscopic lines in this work. Quantities denoted with a dagger ($^\dagger$) are from \citetalias{Lohner-Bottcher2019}. All other quantities are from the NIST Atomic Spectra Database \citep{NISTASD}. \label{tab:feI}}
\tablenum{1}

\tablehead{\colhead{Species} & \colhead{Air Wavelength (\AA)} & \colhead{Energy (eV)} & \colhead{Height (km)} & \colhead{$g_{\rm eff}$} & \colhead{$\log(gf)$} & \multicolumn{2}{c}{Spectroscopic Term} & & \multicolumn{2}{c}{Excitation Potential (eV)} \\
\cline{7-8}
\cline{10-11}
& & & & & & Lower & Upper & & Lower & Upper}

\startdata
Fe I & 5434.5232$^\dagger$ & 2.28078418 & 550$^\dagger$ & 0.00$^\dagger$ & -2.122 & 3d$^7$4s \ $^5$F$_1$ & 3d$^6$4s4p \  $^5$D$^{\rm o}_0$ & & 1.01105568 & 3.29183986 \\
\enddata
\end{deluxetable*}

@@

% \input{captions/fig2.tex}

@@

% \input{captions/fig3.tex}

@@

%input{captions/fig4.tex}
\revise{To create synthetic spectra, \grass\ creates disk-resolved line profiles on a uniform spatial grid (as described in \S\ref{sec:resolved_disk}).} The \revise{ideal resolution of this spatial grid over the stellar surface would match that of the input observations. However, because the spatial resolution of the input observations was designed to approximate the typical angular area of supergranules and consequently varies with position on the disk (as described in \S\ref{subsec:input_data}), simulating an ideal grid is impractical.} Therefore, we choose \revise{a rectangular grid and set} $N$ \revise{(the number of grid cells along each Cartesian $xy$ direction in the sky plane) such that the area of the spatial grid cell matches the weighted-average area of the input data observations. Given the sizes of the elliptical oscillations described in \S\ref{subsec:input_data} and \citetalias{Lohner-Bottcher2018}, we compute $N^2\sim132^2$ as our optimized number of grid cells.} \par

@@

\subsection{Synthetic Line Depth and RV Variability} \label{sec:depth_var}
%input{captions/fig5.tex}

@@

%input{captions/fig6.tex}

@@

%input{captions/fig7.tex}

@@

% \input{tables/observations.tex}
\begin{deluxetable}{ccccc}
\tablecaption{\revisetwo{Comparison of observing strategies with a short (30-second) or long (one-hour) wait between observations within a night (see Figure \ref{fig:obs}). Two-sample KS tests fail to reject the null hypothesis that the observed velocity distributions are drawn from the same parent distributions.} \label{tab:obs}} 
\tablenum{2}

\tablehead{\colhead{$N_{\rm obs}$} & \colhead{$p$-value} & \colhead{KS-statistic} & \multicolumn{2}{c}{RMS $(\ms)$} \\
\cline{4-5}
& & & Short Wait & Long Wait}

\startdata
2 & 0.578 & 0.779 & 0.184 & 0.191 \\
3 & 0.893 & 0.577 & 0.144 & 0.147  \\
4 & 0.441 & 0.866 & 0.117 & 0.125  \\
\enddata
\end{deluxetable}
